%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Long Professional Curriculum Vitae
% LaTeX Template
% Version 1.1 (9/12/12)
%
% This template has been downloaded from:
% http://www.latextemplates.com
%
% Original author:
% Rensselaer Polytechnic Institute (http://www.rpi.edu/dept/arc/training/latex/resumes/)
%
% Important note:
% This template requires the res.cls file to be in the same directory as the
% .tex file. The res.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[10pt]{res} % Use the res.cls style, the font size can be changed to 11pt or 12pt here

\usepackage{helvet} % Default font is the helvetica postscript font
%\usepackage{newcent} % To change the default font to the new century schoolbook postscript font uncomment this line and comment the one above

\newsectionwidth{0pt} % Stops section indenting

\begin{document}

%----------------------------------------------------------------------------------------
%	YOUR NAME AND ADDRESS(ES) SECTION
%----------------------------------------------------------------------------------------

\name{Bastian Gruber\\ \\} % Your name at the top

% If you don't want one of the addresses, simply remove all the text in the first or second \address{} bracket

\address{{\bf Professional} \\ LinkedIn: linkedin.com/in/bastiangruber \\ Project: rustwebdevelopment.com \\ E-Mail: gruberbastian@me.com}

\address{{\bf Code} \\ GitHub: github.com/gruberb \\ } % Your address 2

%----------------------------------------------------------------------------------------

\begin{resume}

%----------------------------------------------------------------------------------------
%	OBJECTIVE SECTION
%----------------------------------------------------------------------------------------

\section{\centerline{SUMMARY}}

\vspace{8pt} % Gap between title and text
Passionate Software Engineer and published Author ("Rust Web Development" - Manning). I have over 10 years of experience working in many roles (Tech Lead, Customer Facing, Systems Engineer, Frontend and Backend), in multiple companies (StartUps with 3-8 people, small businesses with around 50 people and large scale enterprise from 200 to 5.000 people). I organize community events (Rust and Tell Berlin, besides others). I am considered a great team player, and lover of software.


%----------------------------------------------------------------------------------------
 
\vspace{0.2in} % Some whitespace between sections

%----------------------------------------------------------------------------------------
%	PROFESSIONAL EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{\centerline{PROFESSIONAL EXPERIENCE}} 

\vspace{8pt} % Gap between title and text

{\sl Senior Systems Engineer - Full-time} \hfill April 2023 - now \\
Toposware, Remote \\
Developing a Peer-to-Peer distributed network, with high throughput and low latency. Developing the protocol and the services in-house.
\begin{itemize} \itemsep -2pt % Reduce space between items
\item Working in a small, tight group of engineers
\item Writing specifications and RFCs 
\item Implementing the p2p protocol on top of libp2p in Rust
\item Ten-folding the throughput from the initial implementation
\item Project management, Pull Requests and Issues are all open source
\item Setting up GitHub CI/CD pipelines
\end{itemize}

{\sl Senior Software Engineer - Full-time} \hfill August 2022 - February 2023 \\
Centrifuge, Remote \\
Centrifuge works on equalising access to financial products. We create the opportunity to move pooling of funds for loans away from banks-only, and give the chance for small business to apply for loans through our protocol, and for more than one investor to invest in these loans. We use the Polkadot ecosystem to build our product as a base layer.
\begin{itemize} \itemsep -2pt % Reduce space between items
\item Working in a self-managed organisation wearing different heads (Head of Documentation, Protocol Engineer)
\item Writing specifications and RFCs 
\item Implemented the Centrifuge protocol with Rust
\item Building out a runtime on top of Substrate
\item Project management, Pull Requests and Issues were all open source
\item Setting up GitHub CI/CD pipelines
\end{itemize}

{\sl Sr. Solutions Architect (Professional Services) - Full-time} \hfill June 2020 - August 2022 \\
Twilio Inc., Remote \\
Twilio just started to create their Professional Services team in EMEA and I was the second SA joining their team. The goal is to support and enable small to large scale customers using the Twilio APIs, help them integrate the services, do code reviews and review their architecture.
\begin{itemize} \itemsep -2pt % Reduce space between items
\item Acted as the Technical Lead inside Fortune 500 companies
\item Involved in hiring and onboarding
\item Creating architectural specifications
\item Develop reusable deliverables for customers
\item Leading customers through a technical solution
\item Code reviews
\item Setting up sales and feedback cycles
\end{itemize}

{\sl Author of "Rust Web Development" } \hfill October 2020 - December 2022 \\
Manning Publications, Remote\\
Writing the book "Rust Web Development". Research, writing and marketing the book in partnership with Manning. 
\begin{itemize} \itemsep -2pt % Reduce space between items
\item Selling 3k copies in the first 12 months
\item Interviewed by 5 podcasts
\item Teaching concepts from what a runtime is to how to deploy an efficient Rust code base
\item Copy editing and marketing through different channels
\item Held a Reddit AMA to answer questions from readers and Rustaceans
\end{itemize}
 
{\sl Systems Engineer - Contract} \hfill September 2019 - May 2020 \\
Kraken Digital Currency Exchange, Remote (San Francisco)\\
Part of the first Rust team of the company, replacing the core trading engine with Rust. Worked alongside 12 highly experienced Software Developers from all over the world. Refactor code from PHP to Rust, wrote new features in Rust in a well-tested highly secure manner.
\begin{itemize}
	\item Re-wrote several PHP services in Rust to increase the throughput 100fold 
	\item Wrote new services in Rust from the ground up
	\item Cross-communication with different teams and the CTO
\end{itemize}

{\sl Software Engineer, Tech Lead} \hfill September 2010 -- August 2019 \\
Scholarship, Enterprise, StartUp\\

\begin{itemize}
	\item Was the first employee in two companies, setting up infrastructure, processes and the tech stack
	\item Worked both as a freelance consultant and full time employee
	\item Guided teams through learning a new language and maintaining a new technology stack
	\item Integrated security related infrastructure for IoT companies
	\item Mentored and guided junior developers
\end{itemize}

\section{\centerline{EDUCATION}} 

\vspace{8pt} % Gap between title and text

{\sl Bachelor of Science, Computer Science} \hfill September 2010 - February 2014 \\
TH Ingolstadt\\
Scholarship from Allianz Deutschland AG to study Computer Science, fully funded and with trainings in Scrum, Java, PL/I and mainframe systems on the side.



\end{resume} 
\end{document}